ResultsNPS

### 2019-10-10 R/scripts/resultsNPS.Rmd

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: medium
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')

quant_max <- 0.95
size <- params$size

# alternative 1:
# exp_list <- c('IT000125_20190808', 'IT000125_20190812')
# df_original <- compare_sto$get_df_comparison(exp_list)
# df_original %<>% filter(scenario=='numparalleltasks_3' | experiment==1)
# alternative 2:
# compare_sto <- get_compare_sto()
# df_original <- compare_sto$get_instances[[size]]()
# df <- df_original %>% mutate(experiment=if_else(experiment==0, 'cuts', 'base'))
# alternative 3:
df <- do.call(params$size, args=list())
# df <- get_4_tasks_aggressive()

@@

quality_perf <- get_quality_perf(df)
mean_dif <- quality_perf$dif_perc %>%  mean
per_cut <- sum(quality_perf$dif_perc<0)/length(quality_perf$dif_perc)

@@

In addition, in `r (per_cut*100) %>% round(2)`\% of instances (`r (quality_perf_nrow*per_cut) %>% floor` of `r quality_perf_nrow`) the `cuts` model outperform the solution from the base model.

@@

mean_times <- 
    comparison_table %>% 
    group_by(experiment) %>% 
    summarise(time_mean = mean(time), 
              time_medi = median(time)) %>% 
    aux_compare

>>>>

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: get_3_tasks_aggresive_perc_add
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')
source('functions/datasets_NPS.R')
quant_max <- 0.95
size <- params$size

# alternative 1:
# exp_list <- c('IT000125_20190808', 'IT000125_20190812')
# df_original <- compare_sto$get_df_comparison(exp_list)
# df_original %<>% filter(scenario=='numparalleltasks_3' | experiment==1)
# alternative 2:
# compare_sto <- get_compare_sto()
# df_original <- compare_sto$get_instances[[size]]()
# df <- df_original %>% mutate(experiment=if_else(experiment==0, 'cuts', 'base'))
# alternative 3:
df <- do.call(size, args=list())
# df <- get_4_tasks_aggressive()

@@

quality_perf <- get_quality_perf(df)
mean_dif <- quality_perf$dif_perc %>%  mean
per_cut <- sum(quality_perf$dif_perc<0)/length(quality_perf$dif_perc)
q95_cut <- quality_perf$dif_perc %>% quantile(0.95)

@@

In addition, in `r (per_cut*100) %>% round(2)`\% of instances (`r (quality_perf_nrow*per_cut) %>% floor` of `r quality_perf_nrow`) the `cuts` model outperform the solution from the base model. 95\% of instances are less than `r q95_cut %>% round(2)`\% away from the best known solution.

@@

mean_times <- 
    comparison_table %>% 
    group_by(scenario, experiment) %>% 
    summarise(time_mean = mean(time), 
              time_medi = median(time)) %>% 
    aux_compare
